### 2021-11-11 response/response.tex

Yes, it is true that when we consider the experimental observations of a qunatum Hall system a strong dressing field can increase the temperature of the sample. However, as mentioned in previous study by Dini \textit{et al.} \cite{dini16} and Kibis \textit{et al.} \cite{kibis15}, we can maintain low temperature by applying narroaw pulses of a strong dressing field to observe the discussed phenomena.

Although we have extend our general derivation given in Eq.~[31] into special consideration for comparison, we can improve our theoritical model into different type of partical distribution functions. As discussed by Dmitriev \textit{et al.} \cite{dmitriev05}, a well-defined analytical discussion need to address the changes in distribution functions in our derived general longitudinal conductivity formula and this would be an interesting extension to our study.

\subsubsection*{Comment 6 -
\color{RoyalBlue} The authors presented the results for the conductivity tensor's xx- and yy-components. They seem to be identical, apart of a dimensional factor $(eB)^2$ in the denominator. The equality of these two components is expected for isotropic systems. Does the polarization of the electromagnetic field break the isotropy? Do the two components of the conductivity remain equal even for an arbitrary direction of a linearly polarized field? Is there a non-Hall contribution to the xy-component?
}

We thank the reviewer for pointing out the importance mistake we have made in the $yy$-component calculation. We have made an mistake in the current operator calculations and this has leaded to a unexpected normalization factor in the conductivity expresiion. Since we have only analyzed the $xx$-component this is not used to any further calculations and remaining analysis is not effected by this change. After this changes we can predict that the both $xx$-component and $yy$-component shows the same conductivity behaviours. We added these changes to the calculations done in Appendix D and the conductivity calculation under Section V.

\begin{itemize}
  \item Appendix D - (page 14):\\
  {\color{Maroon}
  \subsection*{\label{appendix_d}Current operators for a dressed quantum Hall system}

  In this section, we derive the current density operator for the $N$-th Landau level in a dressed quantum Hall system. We already found the exact solution for the time-dependent Schrödinger equation with the Hamiltonian give in Eq.~(1) and we identified them as the Floquet states in Eq.~(14). For the simplicity of notation, we can represent the Floquet modes derived in Eq.~(10) as quantum states using their corresponding quantum numbers as follows
  \begin{equation} \tag{D1}
    \ket{\phi_{n,m}} = \ket{n,k_x}.
  \end{equation}
  Using this complete set of quantum states \cite{wackerl20,holthaus15,grifoni98}, we can represent the single particle current operator's matrix element as
  \begin{equation} \tag{D2}
    \left(\vb{j} \right)_{nm,n'm'} = \mel{n,k_x}{\;\hat{\vb{j}}\;}{n',k'_x}.
  \end{equation}
  Next, we can identify the particle current operator for our system \cite{mahan00,bruus04} as
  \begin{equation} \tag{D3}
    \hat{\vb{j}} = \frac{1}{\widetilde{m}} \left\{\hat{\vb{p}} - e\left[\vb{A}_s + \vb{A}_d(t) \right]\right\},
  \end{equation}
  where $\widetilde{m}$ is the mass of the considering particle.

  First, we consider the $x$-directional particle current operator component, and we can identify that as
  \begin{equation} \tag{D4}
    \hat{j}_x = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{x} + eBy \right).
  \end{equation}
  Next, we calculate the matrix elements of $x$-directional current operator against our Floquet mode basis
  \begin{equation} \tag{D5}
    \left({j}_x \right)_{nm,n'm'} =
    \mel{n,k_x}{\;\frac{1}{\widetilde{m}} \left(-i\hbar\pdv{x} + eBy \right)}{n',k'_x},
  \end{equation}
  and we evaluate these using the Floquet modes derived in Eq.~(7) as follows
  \begin{equation} \tag{D6}
    \begin{aligned}
      \left({j}_x \right)_{nm,n'm'} = &
      \frac{1}{{\widetilde{m}}}
      \delta_{k_x,k'_x}
      \int
      \left(\hbar k'_x + eBy\right) \\
      & \times
       \chi_{n}\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
      \chi_{n'}\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
      dy.
    \end{aligned}
  \end{equation}
  Let $[y - y_0 - \zeta(t)] = \bar{y}$ and we can obtain
  \begin{equation} \tag{D7}
    \begin{aligned}
      \left({j}_x \right)_{nm,n'm'} =
      \frac{1}{{\widetilde{m}}}
      \delta_{k_x,k'_x}
      \int &
      \left[ \hbar k'_x + eB\bar{y} -\hbar k'_x + eB\zeta(t)\right]
      \chi_{n}(\bar{y})
      \chi_{n'}(\bar{y})
      d\bar{y}.
    \end{aligned}
  \end{equation}
  Using the following integral identities of the Floquet modes which are made up with Gauss-Hermite functions \cite{vedenyapin11,szego59}
  \begin{equation} \tag{D8}
    \int
    \chi_{n}({y})
    \chi_{n'}({y}) d{y} =
    \kappa\delta_{n',n},
  \end{equation}
  \begin{equation} \tag{D9}
    \int
    y \chi_{n}({y})\chi_{n'}({y}) d{y} =
    \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
    \delta_{n',n-1} \right),
  \end{equation}
  we simplify the matrix elements of $x$-directional current operator to obtain
  \begin{equation} \tag{D10}
    \begin{aligned}
      &\left({j}_x \right)_{nm,n'm'} =
      \frac{eB}{{\widetilde{m}}}
      \delta_{k_x,k'_x}
      \left[
      \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
      \delta_{n',n-1}\right)
      + \zeta(t) \delta_{n',n}
      \right].
    \end{aligned}
  \end{equation}
  Due to high complexity of extract solution, in this study we only consider the constant contribution. Therefore, we can identify the $0$-th component of the Fourier series as
  \begin{equation} \tag{D11}
    \begin{aligned}
        \left({j}_x \right)_{nm,n'm'} =&
        \frac{eB}{\widetilde{m}}
        \delta_{k_x,k'_x}
        \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
        \delta_{n',n-1} \right).
    \end{aligned}
  \end{equation}
  For a electric current operator, we can apply the electron's charge and the  effective mass of the electron to the above derived equation. This leads to
  \begin{equation} \tag{D12}
    \begin{aligned}
        \Big({j}^x_{s=0}\Big)_{nm,n'm'}^{electron}  =&
        \frac{e^2B}{{m_e}}
        \delta_{k_x,k'_x}
        \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
        \delta_{n',n-1} \right).
    \end{aligned}
  \end{equation}

  Moreover, we can identify the $y$-directional current operator component as
  \begin{equation} \tag{D13}
    \hat{j}_y = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{y} - \frac{eE}{\omega}\cos(\omega t) \right).
  \end{equation}
  Using this operator, we can represent the matrix elements of $y$-directional current operator in Floquet mode basis as
  \begin{equation} \tag{D14}
    \left({j}_y \right)_{nm,n'm'} =
    \mel{n,k_x}{\;\frac{-1}{\widetilde{m}} \left(i\hbar\pdv{y} + \frac{eE}{\omega}\cos(\omega t) \right)}{n',k'_x}.
  \end{equation}
  After following the same steps done for the $x$-directional current operator, and recursion relation of the first derivative of Gauss-Hermite functions
  \begin{equation} \tag{D15}
    \begin{aligned}
      \pdv{\chi_{n}({y})}{y} =
      \kappa\left[
      -  \sqrt{\frac{n+1}{2}} \chi_{n+1}({y})
      +  \sqrt{\frac{n}{2}} \chi_{n - 1}({y})
      \right],
    \end{aligned}
  \end{equation}
  we can identify the $0$-th component of matrix elements for $y$-directional electric current operator as
  \begin{equation} \tag{D16}
    \begin{aligned}
      \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{electron} = &
      \frac{ie\hbar\kappa^2}{m_e}
      \delta_{k_x,k'_x}
      \left(
      \sqrt{\frac{n}{2}} \delta_{n',n-1}
      - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
      \right).
    \end{aligned}
  \end{equation}
  \begin{equation} \tag{D17}
    \begin{aligned}
      \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{electron} = &
      \frac{ie^2 B}{m_e}
      \delta_{k_x,k'_x}
      \left(
      \sqrt{\frac{n}{2}} \delta_{n',n-1}
      - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
      \right).
    \end{aligned}
  \end{equation}
  }
  \item Section V - (page 7):\\
  {\color{Maroon}
  Following the same steps as above derivation, we can derive the longitudinal conductivity in the $y$-direction by applying the electric current operator for $y$-direction derived in Appendix D
  \begin{equation} \tag{36}
    \begin{aligned}
      {\sigma}^{yy} =
      \frac{e^2}{\pi\hbar A} &
      \sum_{n}
      \frac{(n+1)}{\gamma_{n}\gamma_{n+1}}
      \left[
        \frac{1}
        {
          1 + \left(\frac{X_F - n -1}{\gamma_{n+1}}\right)^2
        }
      \right]
      \left[
        \frac{1}
        {
          1 + \left(\frac{X_F - n}{\gamma_{n}}\right)^2
        }
      \right].
    \end{aligned}
  \end{equation}
  }
\end{itemize}

% For analysing our system, we mainly employ the Floquet-Drude conductivity formula introduced by Wackerl \textit{et al.} \cite{wackerl20}. The Floquet-Drude conductivity formula was only developed for the diogonal components of the conductivity tensor of the considering system. In this analysis we were only focused on SdH oscillations in longitudinal conductivity components we analysed the dressing field effect on two diogonal components of the conductivity tensor.
%
% As mentioned in Ref.\cite{wackerl20} and our work, applied strong dressing field tends to change the qunatum state of the consideirng system and creates novel states called Floquet states. The propeties of these states are depends on the characteristics of applied dressing field. Therefore, the polarization method also change the behavior of the Floquet states.
% These polarization dependent conductivity behaviors in 2DEG systems can be found in references \cite{wackerl20,morina15} and in their work authors have illustrated the conductivity behavior with circular and linear polarized dressing fields. In addition, they have mentioned the impact on the direction of the linearly polarization dressing field and this will break the isotropy behaviour of the longitudinal conductivities in the consideirng system.
%
% We also followed the same formalism of Floquet states for 2DEG quantum Hall systems. In our work also we were able to identify that the applied dressing field's polarization direction can be effect the magnitude of the longitudinal conductivity component. A detailed derivation of these two longitudinal conductivity component's current operators are given in Appendix D. If we applied a arbitary directional polarized dressing field, we can derive a expression for the longitudinal conductivity components by considering dressing field contribution for each direction ($x$ and $y$) with same steps in this analysis. This would change the amplitude of the considering dressing field ($E$) in each direction. However, now there will be a new conponent in parallel to the considering conductivity component and we need to solve the Schrödinger equation with the modified Hamiltonian in Eq.~[2] for the new system with these changes.
% However in our analysis, our main objective was to identify the manipulation capabilities of SdH oscillations using dressing field intensity. In addition, we only consider the longitudinal components in this analysis by extending the Floquet-Drude conductivity formula that derived only for the diogonal components in conductivity tensor. Therefore we are unable to predict the off-diogonal component behavior of the system through our analysis and we need a novel formalism to handle these type of behaviors of dressed 2DEG quanutm Hall systems.

@@

\subsubsection*{Comment 2 -
\color{RoyalBlue} In the presence of disorder, Anderson localization and topologically protected edge modes are dominant considerations when calculating DC transport coefficients. How are these factors taken into account?
}

We agree with the reviewer that the discussion on the Anderson localization and topologically protected edge modes are was missing from the manuscript.
We would like to mentioned the reviewer that while deriving Eq.~[31], we have assumed that the applyed static magnetic field is placed in a lower intensity range where we can neglect a number of effects known to appear in a 2DEG quantum Hall system. Under this condition we can neglect the localization in the tails of Landau level peaks, the formation of the edge states, the electron-electron interactions and the spin splitting as well. As mentioned in the work done by Endo \textit{et al.} \cite{endo09}, under the given magnetic field range, the undressed magnetotransport properties of GaAs/AlGaAs 2DEG quantum Hall system provides excellent agrrement between the experimental observations and theory. The authors of the Ref.\cite{endo09} has neglect the effects mentioned above during the development the theory. We also follwed the same theoritical derivation with given assumtions but with a additionl dressing field. Our results for undressed system gives a better aggrement with the results from Ref.\cite{endo09}, while we provide a better description to manipulate the width of the Landau level conductivity peaks. We have added this clarification in the manuscript.

\begin{itemize}
  \item Section I - sixth paragraph (page 2):\\
  {\color{Maroon}
  It is important to note that, in this analysis we consider the applied magnetic field at a range where the Anderson localization, the formation of the edge states, the spin splitting and the electron–electron interactions can be neglected. The use of this assumption can also be found in study done by  Endo \textit{et al.} \cite{endo09}.
  }
  \item Section VIII - sixth paragraph (page 2):\\
  {\color{Maroon}
  We assumed the impurities in the material as a Gaussian random scattering potential and the applied magnetic field within a order where we can neglect effects of the the Anderson localization, the formation of the edge states, the spin splitting and the electron–electron interactions.
  }
\end{itemize}

### 2021-11-12 response/response.tex

Yes, it is true that when we consider the experimental observations of a qunatum Hall system a strong dressing field can increase the temperature of the sample. However, as mentioned in previous study by Dini \textit{et al.} \cite{dini16} and Kibis \textit{et al.} \cite{kibis15}, we can maintain low temperature by applying narroaw pulses of a strong dressing field to observe the discussed phenomena.

Although we have extend our general derivation given in Eq.~[31] into special consideration for comparison, we can improve our theoritical model into different type of partical distribution functions. As discussed by Dmitriev \textit{et al.} \cite{dmitriev05}, a well-defined analytical discussion need to address the changes in distribution functions in our derived general longitudinal conductivity formula and this would be an interesting extension to our study.

\subsubsection*{Comment 6 -
\color{RoyalBlue} The authors presented the results for the conductivity tensor's xx- and yy-components. They seem to be identical, apart of a dimensional factor $(eB)^2$ in the denominator. The equality of these two components is expected for isotropic systems. Does the polarization of the electromagnetic field break the isotropy? Do the two components of the conductivity remain equal even for an arbitrary direction of a linearly polarized field? Is there a non-Hall contribution to the xy-component?
}

We thank the reviewer for pointing out the importance mistake we have made in the $yy$-component calculation. We have made an mistake in the current operator calculations and this has leaded to a unexpected normalization factor in the conductivity expresiion. Since we have only analyzed the normalized $xx$-component of the conductivity tensor, the remaining analysis is not effected by this change. After this change we can predict that the both $xx$-component and $yy$-component shows the same conductivity behaviours. We added these changes to the calculations done in Appendix D and the conductivity calculation under Section V.

@@

\begin{itemize}
  \item Appendix D - (page 14):\\
  {\color{Maroon}
  \subsection*{\label{appendix_d}Current operators for a dressed quantum Hall system}

  In this section, we derive the current density operator for the $N$-th Landau level in a dressed quantum Hall system. We already found the exact solution for the time-dependent Schrödinger equation with the Hamiltonian give in Eq.~(1) and we identified them as the Floquet states in Eq.~(14). For the simplicity of notation, we can represent the Floquet modes derived in Eq.~(10) as quantum states using their corresponding quantum numbers as follows
  \begin{equation} \tag{D1}
    \ket{\phi_{n,m}} = \ket{n,k_x}.
  \end{equation}
  Using this complete set of quantum states \cite{wackerl20,holthaus15,grifoni98}, we can represent the single particle current operator's matrix element as
  \begin{equation} \tag{D2}
    \left(\vb{j} \right)_{nm,n'm'} = \mel{n,k_x}{\;\hat{\vb{j}}\;}{n',k'_x}.
  \end{equation}
  Next, we can identify the particle current operator for our system \cite{mahan00,bruus04} as
  \begin{equation} \tag{D3}
    \hat{\vb{j}} = \frac{1}{\widetilde{m}} \left\{\hat{\vb{p}} - e\left[\vb{A}_s + \vb{A}_d(t) \right]\right\},
  \end{equation}
  where $\widetilde{m}$ is the mass of the considering particle.

  First, we consider the $x$-directional particle current operator component, and we can identify that as
  \begin{equation} \tag{D4}
    \hat{j}_x = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{x} + eBy \right).
  \end{equation}
  Next, we calculate the matrix elements of $x$-directional current operator against our Floquet mode basis
  \begin{equation} \tag{D5}
    \left({j}_x \right)_{nm,n'm'} =
    \mel{n,k_x}{\;\frac{1}{\widetilde{m}} \left(-i\hbar\pdv{x} + eBy \right)}{n',k'_x},
  \end{equation}
  and we evaluate these using the Floquet modes derived in Eq.~(7) as follows
  \begin{equation} \tag{D6}
    \begin{aligned}
      \left({j}_x \right)_{nm,n'm'} = &
      \frac{1}{{\widetilde{m}}}
      \delta_{k_x,k'_x}
      \int
      \left(\hbar k'_x + eBy\right) \\
      & \times
       \chi_{n}\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
      \chi_{n'}\bm{\left(}y - y_0 - \zeta(t)\bm{\right)}
      dy.
    \end{aligned}
  \end{equation}
  Let $[y - y_0 - \zeta(t)] = \bar{y}$ and we can obtain
  \begin{equation} \tag{D7}
    \begin{aligned}
      \left({j}_x \right)_{nm,n'm'} =
      \frac{1}{{\widetilde{m}}}
      \delta_{k_x,k'_x}
      \int &
      \left[ \hbar k'_x + eB\bar{y} -\hbar k'_x + eB\zeta(t)\right]
      \chi_{n}(\bar{y})
      \chi_{n'}(\bar{y})
      d\bar{y}.
    \end{aligned}
  \end{equation}
  Using the following integral identities of the Floquet modes which are made up with Gauss-Hermite functions \cite{vedenyapin11,szego59}
  \begin{equation} \tag{D8}
    \int
    \chi_{n}({y})
    \chi_{n'}({y}) d{y} =
    \delta_{n',n},
  \end{equation}
  \begin{equation} \tag{D9}
    \int
    y \chi_{n}({y})\chi_{n'}({y}) d{y} =
    \frac{1}{\kappa}
    \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
    \delta_{n',n-1} \right),
  \end{equation}
  we simplify the matrix elements of $x$-directional current operator to obtain
  \begin{equation} \tag{D10}
    \begin{aligned}
      &\left({j}_x \right)_{nm,n'm'} =
      \frac{eB}{{\widetilde{m}\kappa}}
      \delta_{k_x,k'_x}
      \left[
      \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
      \delta_{n',n-1}\right)
      + \zeta(t) \delta_{n',n}
      \right].
    \end{aligned}
  \end{equation}
  Due to high complexity of extract solution, in this study we only consider the constant contribution. Therefore, we can identify the $0$-th component of the Fourier series as
  \begin{equation} \tag{D11}
    \begin{aligned}
        \left({j}_x \right)_{nm,n'm'} =&
        \frac{eB}{\widetilde{m}\kappa}
        \delta_{k_x,k'_x}
        \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
        \delta_{n',n-1} \right).
    \end{aligned}
  \end{equation}
  For a electric current operator, we can apply the electron's charge and the  effective mass of the electron to the above derived equation. This leads to
  \begin{equation} \tag{D12}
    \begin{aligned}
        \Big({j}^x_{s=0}\Big)_{nm,n'm'}^{electron}  =&
        \frac{e\hbar}{{m_e}l_0}
        \delta_{k_x,k'_x}
        \left(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
        \delta_{n',n-1} \right).
    \end{aligned}
  \end{equation}
  where $l_0 = \sqrt{\flatfrac{\hbar}{eB}}$ is the magnetic length.

  Moreover, we can identify the $y$-directional current operator component as
  \begin{equation} \tag{D13}
    \hat{j}_y = \frac{1}{\widetilde{m}} \left(-i\hbar\pdv{y} - \frac{eE}{\omega}\cos(\omega t) \right).
  \end{equation}
  Using this operator, we can represent the matrix elements of $y$-directional current operator in Floquet mode basis as
  \begin{equation} \tag{D14}
    \left({j}_y \right)_{nm,n'm'} =
    \mel{n,k_x}{\;\frac{-1}{\widetilde{m}} \left(i\hbar\pdv{y} + \frac{eE}{\omega}\cos(\omega t) \right)}{n',k'_x}.
  \end{equation}
  After following the same steps done for the $x$-directional current operator, and recursion relation of the first derivative of Gauss-Hermite functions
  \begin{equation} \tag{D15}
    \begin{aligned}
      \pdv{\chi_{n}({y})}{y} =
      \kappa\left[
      -  \sqrt{\frac{n+1}{2}} \chi_{n+1}({y})
      +  \sqrt{\frac{n}{2}} \chi_{n - 1}({y})
      \right],
    \end{aligned}
  \end{equation}
  we can identify the $0$-th component of matrix elements for $y$-directional electric current operator as
  \begin{equation} \tag{D16}
    \begin{aligned}
      \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{electron} = &
      \frac{ie\hbar\kappa}{m_e}
      \delta_{k_x,k'_x}
      \left(
      \sqrt{\frac{n}{2}} \delta_{n',n-1}
      - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
      \right).
    \end{aligned}
  \end{equation}
  \begin{equation} \tag{D17}
    \begin{aligned}
      \Big({j}^y_{s=0}\Big)_{nm,n'm'}^{electron} = &
      \frac{ie \hbar}{m_e l_0}
      \delta_{k_x,k'_x}
      \left(
      \sqrt{\frac{n}{2}} \delta_{n',n-1}
      - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
      \right).
    \end{aligned}
  \end{equation}
  }
  \item Section V - (page 7):\\
  {\color{Maroon}
  Moreover, let $\Pi = \varepsilon_F$ and the derived expression in Eq.~(31) leads to
  \begin{equation} \label{eq:35}
    \begin{aligned}
      \sigma^{xx}  =
      \frac{e^2l_0^2}{\pi\hbar A}
      \sum_{n}
      \frac{(n+1)}{\gamma_{n}\gamma_{n+1}}
      \left[
        \frac{1}
        {
          1 + \left(\frac{X_F - n -1}{\gamma_{n+1}}\right)^2
        }
      \right]
      \left[
        \frac{1}
        {
          1 + \left(\frac{X_F - n}{\gamma_{n}}\right)^2
        }
      \right],
    \end{aligned}
  \end{equation}
  where $X_F = \left[\flatfrac{\varepsilon_F}{(\hbar \omega_0)} - \flatfrac{1}{2}\right]$,
  $\gamma_n = \flatfrac{\widetilde{{\Gamma}}(\varepsilon_n)}{(\hbar \omega_0)}$, and $l_0 = \sqrt{\flatfrac{\hbar}{eB}}$.
  Following the same steps as above derivation, we can derive the longitudinal conductivity in the $y$-direction by applying the electric current operator for $y$-direction derived in Appendix D
  \begin{equation} \label{eq:36}
    \begin{aligned}
      {\sigma}^{yy} =
      \frac{e^2l_0^2}{\pi\hbar A}
      \sum_{n}
      \frac{(n+1)}{\gamma_{n}\gamma_{n+1}}
      \left[
        \frac{1}
        {
          1 + \left(\frac{X_F - n -1}{\gamma_{n+1}}\right)^2
        }
      \right]
      \left[
        \frac{1}
        {
          1 + \left(\frac{X_F - n}{\gamma_{n}}\right)^2
        }
      \right].
    \end{aligned}
  \end{equation}
  }
\end{itemize}

@@

\begin{itemize}
  \item Section I - sixth paragraph (page 2):\\
  {\color{Maroon}
  It is important to note that, in this analysis we consider the applied magnetic field at a range where the Anderson localization, the formation of the edge states, the spin splitting and the electron–electron interactions can be neglected. The use of this assumption can also be found in study done by  Endo \textit{et al.} \cite{endo09}.
  }
  \item Section VIII - sixth paragraph (page 2):\\
  {\color{Maroon}
  We assumed the impurities in the material as a Gaussian random scattering potential and the applied magnetic field within a order where we can neglect effects of the the Anderson localization, the formation of the edge states, the spin splitting and the electron–electron interactions.
  }
\end{itemize}

\subsubsection*{Comment 3 -
\color{RoyalBlue} Can the authors reproduce the quantized Hall conductance of filled Landau levels in the presence of disorder? Please discuss.
}

For analysing our system, we mainly employ the Floquet-Drude conductivity formula introduced by Wackerl \textit{et al.} \cite{wackerl20}. The Floquet-Drude conductivity formula was only developed for the diogonal components of the conductivity tensor of the considering system. In this analysis we were only focused on SdH oscillations in longitudinal conductivity components we analysed the dressing field effect on two diogonal components of the conductivity tensor through Floquet-Drude conductivity formula. Therefore we are unable to predict the off-diogonal component behavior of the system through our analysis and we need a novel formalism to handle these type of behaviors of dressed 2DEG quanutm Hall systems. However, we can use the already established formalism introduced by Endo \textit{et al.} \cite{endo09} to predict the behaviour of off-diogonal components of the conductivity tensor. As mentioned in the Ref.~\cite{endo09}, this theory on the relation between longitudinal and transverse conductivities highly match with the experiment observations
\begin{equation} \nonumber
  \dv{\widetilde{\sigma}^{xy}(X_F,I)}{B} \approx
    \pi\mu \frac{\hbar \omega_0}{\varepsilon_F} [\widetilde{\sigma}^{xx}(X_F,I)]^2.
\end{equation}
By comparing the resultion between longitudinal and transverse conductivities in 2DEG quantum Hall system, we can expect the same Hall conductivity behaviour in a dressed quantum Hall system. However, using the dressing field we are able to squeeze the conductivity peaks on Landau levels. This will reduce the region of high conductivity peaks placed near the Landau levels. This will imply sudden Hall conductivity transitions between one plateau to another one near a Landau level. As empherical observation showed in Ref. \cite{klitzing80,gusynin06}, we can predict a staircase behavior for quantum Hall conductivity but with higher intensity dressing field we will get rapid transitions then the undressed system. However, to derive an analytical expression for the quantum Hall conductivity through Floquet-Drude conductivity needs to be reformulate from the begin and it will be the subject of our future study.

@@

\subsubsection*{Comment 4 -
\color{RoyalBlue} The way some previous works are cited is disappointing. Example from page 8: “Despite this behavior being identified in previous works, their results did not coincide with the more accurate description of conductivity components in undressed quantum Hall systems.” This is not informative. Where, specifically, did results from earlier works fall short of reality, which have been better addressed in this work?
}

We would like to thank the reviewer for pointing out the deficiencies on our manuscript and we have considered your recommendations seriously. We made the following changes in language and presentation to improve the clarity of our manuscript.

\begin{itemize}
  \item Section VIII (page 8):\\
  {\color{Maroon}
  Our derived analytical expressions disclosed that we are able to control the transport characteristics of the dressed quantum Hall system by the applied dressing field’s intensity. Using detailed numerical calculations with empirical system parameters, we further analyzed the manipulation of conductivity components using the dressing field.
  We found that the graphical illustrations that we obtained from these numerical calculations are capable of producing the same behavior as experiments on quantum Hall systems in the absence of a dressing field.
  Furthermore, we identified that by increasing the intensity of the radiation, we can squeeze the conductivity regions near the Landau levels. Despite this behavior being identified in previous works done by Dini \textit{et al.}  \cite{dini16}, their results did not coincide with the experimental observations of longitudinal conductivity components in undressed quantum Hall systems presented in Ref.\cite{endo09}. This is due to the fact that the authors of Ref.\cite{dini16} has been used the conventinal expression of longitudinal conductivity from Ref.\cite{ando74_1,ando82}. However this theory yields a semi-elliptical broadening, which significantly deviates by the experimentally observed Landau levels \cite{endo09}.
  However, our generalized analysis on the conductivity of dressed quantum Hall systems provide a well-suited description for empherically observed behaviours of undressed quantum Hall systems as well.
  }
  \item Section III (page 3):\\
  {\color{Maroon}
  The Floquet-Drude conductivity theory was employed recently by Wackerl \textit{et al.} \cite{wackerl20} as a method to analyze the transport properties of quantum systems exposed to strong radiation.
  In their study \cite{wackerl20}, the authors have presented more accurate results than the former theoretical descriptions \cite{morina15,pervishko15} for the conductivity of nanoscale systems in the  presence of a dressing field. Therefore, we apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.
  }
\end{itemize}

### 2021-11-12 response/response.tex

\subsubsection*{Comment 4 -
\color{RoyalBlue} The way some previous works are cited is disappointing. Example from page 8: “Despite this behavior being identified in previous works, their results did not coincide with the more accurate description of conductivity components in undressed quantum Hall systems.” This is not informative. Where, specifically, did results from earlier works fall short of reality, which have been better addressed in this work?
}

We would like to thank the reviewer for pointing out the deficiencies on our manuscript and we have considered your recommendations seriously. We made the following changes in language and presentation to improve the clarity of our manuscript.

\begin{itemize}
  \item Section VIII (page 8):\\
  {\color{Maroon}
  Our derived analytical expressions disclosed that we are able to control the transport characteristics of the dressed quantum Hall system by the applied dressing field’s intensity. Using detailed numerical calculations with empirical system parameters, we further analyzed the manipulation of conductivity components using the dressing field.
  We found that the graphical illustrations that we obtained from these numerical calculations are capable of producing the same behavior as experiments on quantum Hall systems in the absence of a dressing field.
  Furthermore, we identified that by increasing the intensity of the radiation, we can squeeze the conductivity regions near the Landau levels. Despite this behavior being identified in previous works done by Dini \textit{et al.}  \cite{dini16}, their results did not coincide with the experimental observations of longitudinal conductivity components in undressed quantum Hall systems presented in Ref.\cite{endo09}. This is due to the fact that the authors of Ref.\cite{dini16} has been used the conventinal expression of longitudinal conductivity from Ref.\cite{ando74_1,ando82}. However this theory yields a semi-elliptical broadening, which significantly deviates by the experimentally observed Landau levels \cite{endo09}.
  However, our generalized analysis on the conductivity of dressed quantum Hall systems provide a well-suited description for empherically observed behaviours of undressed quantum Hall systems as well.
  }
  \item Section III (page 3):\\
  {\color{Maroon}
  The Floquet-Drude conductivity theory was employed recently by Wackerl \textit{et al.} \cite{wackerl20} as a method to analyze the transport properties of quantum systems exposed to strong radiation.
  In their study \cite{wackerl20}, the authors have presented more accurate results than the former theoretical descriptions \cite{morina15,pervishko15} for the conductivity of nanoscale systems in the  presence of a dressing field. Therefore, we apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.
  }
  \item Section I (page 2):\\
  {\color{Maroon}
  In contrast, we can observe more exciting phenomena by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
  Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, these studies  have not been utilized to describe the optical manipulation of charge transport.
  Recently, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall systems. However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system. The authors of Ref.\cite{dini16} used the conductivity models from Refs. \cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.
  }
  \item Section IV (page 5):\\
  {\color{Maroon}
  Next, we calculated the normalized energy band broadening against $x$-directional momentum component ${k_x}$ for different Landau levels ($N = 0,1,2,3,4$) for GaAs-based quantum well and the results are depicted in Fig.~3 and Fig.~4. To make a comparison, we have selected the experiment parameters to match with the analysis done in Ref.~\cite{endo09}.
  In the study presented in Ref.~\cite{endo09}, the authors have assumed that the effective mass of the electron in GaAs-based quantum well system is $m_e \approx 0.07\widetilde{m}_e$ where $\widetilde{m}_e$ is the mass of the electron \cite{endo09,winkler03,wackerl20}.
  }
\end{itemize}
